Modeling the near-wake of a vertical-axis cross-flow turbine with 2-D and 3-D RANS

### 2015-09-03 paper.tex
Add time to 3-D vorticity caption
Add centering to 2-D vorticity fig
Make note of 3-D DS vortex

Visualizing the complicated wake generated by the turbine is presented for the
2-D and 3-D Spalart--Allmaras cases in Figure~\ref{fig:vorticity-3D} and
Figure~\ref{fig:vorticity-3D}, respectively. It can be seen how the upstream
blade---as it turns back into the streamwise direction---is shedding a large
amount of spanwise vorticity due to the separated flow. In the 3-D case, strong
tip vortices are also present, which trace the ``contracting'' wake flow on the
$-y$ side of the turbine associated with the induced vertical velocity field.

@@

\begin{figure}
    \includegraphics[width=0.8\textwidth]{figures/3D_vorticity_SA_964_10-threshold}

    \caption{Iso-vorticity contours colored by the streamwise component of
        vorticity for the 3-D Spalart--Allmaras case.}

>>>>

Visualizing the complicated wake generated by the turbine is presented for the
2-D and 3-D Spalart--Allmaras cases in Figure~\ref{fig:vorticity-3D} and
Figure~\ref{fig:vorticity-3D}, respectively. It can be seen how the upstream
blade---as it turns back into the streamwise direction---is shedding a large
amount of spanwise vorticity due to the separated flow. In the 3-D case, strong
tip vortices are also present, which trace the ``contracting'' wake flow on the
$-y$ side of the turbine associated with the induced vertical velocity field.
The 3-D dynamic stall vortex also shows assymmetry about the $x$--$y$ mid-rotor
plane; once again highlighting the importance of three-dimensional effects on
wake dynamics.

@@

    \includegraphics[width=0.8\textwidth]{figures/3D_vorticity_SA_964_10-threshold}

    \caption{Iso-vorticity contours (at $t=9.64$ s) colored by the streamwise
        component of vorticity for the 3-D Spalart--Allmaras case.}
